\section{French Phrases}

\begin{itemize}

\item{\emph{Bonjour}: Good morning or good day.}

\item{\emph{Bonsoir}: Good Evening.}

\item{\emph{Bonne nuit}: Good Night.}

\item{\emph{Salut}: Hi.}

\item{\emph{Au revoir}: Goodbye}

\item{\emph{Comment \c{c}a va?}: How are you?}

\item{\emph{Pardon}: Sorry}

\item{\emph{\`{A} bient\^{o}t}: See you soon.}

\item{\emph{Merci}: Thank you.}

\item{\emph{Merci beaucoup}: Thanks a lot.}

\item{\emph{De rien}: You are Welcome (No problem).}

\item{\emph{Bienvenue}: Welcome.}

\item{\emph{S'il vous pla\^it}: Please.}

\item{\emph{S'il te pla\^it}: Please (informal).}

\item{\emph{Bisses}: Kisses.}

\item{\emph{Tu me manques}: I miss you (You are missed by me).}

\item{\emph{Je te manque?}: Do you miss me (Am I missed by you)?}

\item{\emph{Il fait beau/froid/chaud}: It is (The weather is)
pleasant/cold/hot.}

\item{\emph{peut-\^etre}: May be.}

\item{\emph{Pas mal}: Not bad.}

\item{\emph{C'est l\`a}: It is there.}

\item{\emph{Bien s\^ur!}: Of course!}

\item{\emph{Moi aussi}: Me too.}

\item{\emph{Tr\`es bien}: Very well.}

\item{\emph{Mais}: But.}

\item{\emph{Oui}: Yes.}

\item{\emph{Non}: No.}

\item{\emph{\c{C}a va}: Ok.}

\item{\emph{Vous pouvez}: Can you?}

\item{\emph{Et toi}: And you.}

\item{\emph{D'o\`u es-tu?}: Where are you from?}

\item{\emph{Excusez-moi}: Excuse me.}

\item{\emph{D'accord}: Okay (I agree).}

\item{\emph{C'est le m\^eme}: It's the same.}

\item{\emph{C'est ne va pas}: It's not working.}

\item{\emph{Allez, au travail}: Go, get to work.}

\item{\emph{\`A la pause}: A break.}

\item{\emph{Et lui}: And him.}

\item{\emph{Je voudrais \dots}: I would like \dots}

\item{\emph{Se d\'etendre}: Relax.}

\item{\emph{\^Etre en forme}: To be in form (to be fit).}

\item{\emph{Bien cordialement}: Regards (formal), yours sincerely.}

\item{\emph{Amitie's}: Regards (informal).}

\item{\emph{Tout va bien?}: Is everything good?}

\item{\emph{Au soleil...}: In the sun...}

\item{\emph{Sous la plauie}: Under th rain.}

\item{\emph{J'ai peur}: I am scared.}

\end{itemize}
