\section{Tenses in French}

There are eight tenses in French:

\begin{itemize}
\item{Pr\'esent - Present}
\item{Imparfait - Imperfect}
\item{Pass\'e simple - Preterite, Simple past}
\item{Pass\'e compos\'e - Present perfect}
\item{Plus-que-parfait - Past perfect}
\item{Pass\'e ant\'erieur - Past anterior}
\item{Futur - Future}
\item{Futur ant\'erieur - Future perfect}
\end{itemize}


\subsection{The Present (Le Pr\'esent)}

The French present tense is similar in usage to the English present tense.
In French, the present tense is used to express all of the following:

\begin{enumerate}

\item{\textbf{Current actions and situations:}\\
Je suis fatigu\'{e}.\\
I am tired.\\\\
Nous allons au march\'{e}.\\
We are going to the market.}

\item{\textbf{Habitual actions:}\\
Il va \`{a} l'\'{e}cole tous les jours.\\
He goes to school every day.\\\\
Je visite des mus\'{e}es le samedi.\\
I visit museums on Saturdays.}

\item{\textbf{Absolute and general truths:}\\
La terre est ronde.\\
The earth is round.\\\\
L'\'{e}ducation est importante.\\
Education is important.}

\item{\textbf{Actions which will occur immediately:}\\
J'arrive !\\
I'll be right there!\\\\
Il part tout de suite.\\
He is leaving right away.}

\item{\textbf{Conditions, such as in si clauses:}\\
Si je peux, j'irai avec toi.\\
If I can, I will go with you.\\\\
Si vous voulez.\\
If you like.}
\end{enumerate}

\noindent The formation is as follows:\\

\textbf{\emph{Subject + Verb Conjugation + Object}}.

\vspace{0.2in}
\noindent \textbf{Negation}\\\\
\textbf{\emph{Subject + ne + Verb Conjugation + pas + Object}}.

\subsection{The Near Future (Le Futur Proche)}

It is used for events which are going to happen in near future.
The formation is as follows:\\

\textbf{\emph{Subject + Aller + Infinitive Verb}}.

\vspace{0.2in}

\noindent \textbf{Negation}\\\\
\textbf{\emph{Subject + ne + Aller + pas + Infinitive Verb}}.

\noindent \textbf{Examples:}\\\\
Je vais voir Luc.\\
I'm going to see Luc.\\\\
Il va arriver.\\
He's going to arrive.\\\\
Nous allons manger.\\
We're going to eat.

\subsection{The Past Compound (Le Pass\'e Compos\'e)}
